---
title: "eda"
output: html_document
date: "2024-01-18"
---

1.Where is the fall-off point in the funnel? Where do people usually get stuck in their
journey and as a result don’t become activated users? How does time relate to users not
moving forward in their journey?

2. How can we group customers together such that we find patterns of incompletion in the
journey?

```{r}
#Read in Data and Libraries
library(tidyverse)
library(lubridate)
library(zoo)
library(summarytools)
library(markovchain)
data <- read.csv("/Users/yusei/OneDrive/Documents/M148/export.csv")
event_def <- read.csv("/Users/yusei/OneDrive/Documents/M148/Event Definitions.csv")
```

1)Cleaning Data 
```{r}
#Clean defenitions for cleaner merge
event_def <- event_def %>% select(!c(journey_id, event_definition_id))

#Left Join 
data_def <- left_join(data, event_def, by = 'event_name')
head(data_def, 200)
```

```{r}
#removing duplicate entries that are at the same exact time stamp
data_def <- data_def %>% group_by(customer_id, event_name) %>% filter(event_timestamp != lag(event_timestamp, default="1"))
data_def <- data.frame(data_def)

#Cleaning time to lubridate time
data_def$event_timestamp <- ymd_hms(data_def$event_timestamp)
```

```{r}
#Cleaning NA Values 
```


2)Exploratory Data Analysis
```{r}
#To answer EDA
combinations <- data %>% group_by(customer_id, account_id) %>% count()
cust <- combinations %>% select(customer_id, account_id) %>% group_by(customer_id) %>%  count()
df <- data.frame(cust)
df <- df[df$n != 1,]
print(nrow(df))
acct <- combinations %>% select(customer_id, account_id) %>% group_by(account_id) %>%  count()
df2 <- data.frame(acct)
df2 <- df2[df2$n != 1,]
print(nrow(df2))
```

```{r}
#More EDA
data_def %>% select(journey_steps_until_end, milestone_number) %>% descr()
```

Question 3. Where is it effective to intervene with an email or promotion code
```{r}
#Cleaning duplicate promotion created entries
data_three <- data_def
 #data_three <- data_three %>% filter(event_name == 'promotion_created' | event_name == 'order_shipped') %>% mutate(lag = lag(event_timestamp, default = NULL)) %>% mutate(diff = event_timestamp - lag) %>% filter(diff > as.difftime(1, units = "secs"))
data_three
#4,830,153 
```

Whats rate of success after promo sent? 
```{r}
#want customers who have received promotions. 
#group into customer id, select customer ids where event_name == promotion created
df1 <- data_three %>% group_by(customer_id) %>% filter(event_name == 'promotion_created' | event_name == 'order_shipped')
df1 %>% group_keys() %>% nrow()
#1,091,509 customers who were sent a promo

df2 <- data_three %>% group_by(customer_id) %>% filter(event_name == 'promotion_created' | event_name == 'order_shipped') %>%  filter(n_distinct(event_name) > 1)
df2 %>% group_keys() %>% nrow()
#231082 customers who completed an order after being sent a promo

df3 <- data_three %>% group_by(customer_id)
df3 %>% group_keys() %>% nrow()
#1665688 customers total

df4 <- data_three %>% group_by(customer_id) %>% filter(event_name == 'order_shipped') 
df4%>% group_keys() %>% nrow()
#320686 customers who completed an order

320686 - 231082
#89604 customers who completed an order unprompted
1665688 - 1359596
#306092 customers were unprompted
```

```{r}
#Test on one Customer for Markov Chain Model
test <- data_three %>% filter(customer_id == '-784961211')
# Create a transition matrix
transitions <- table(test$event_name, lag(test$event_name))
rownames(transitions) <- colnames(transitions) <- unique(test$event_name)
# Normalize the transition matrix
normalized_transitions <- prop.table(as(transitions, "matrix"), margin = 1)
mc <- new("markovchain", transitionMatrix = as(normalized_transitions, "matrix"))
mc
# Print the transition matrix
mc

# Calculate the steady-state distribution
steady_state <- steadyStates(mc)
steady_state
```

```{r}
#Markov Chain Model For Event Name
# Create a transition matrix
transitions <- table(data_three$event_name, lag(data_three$event_name))
rownames(transitions) <- colnames(transitions) <- unique(data_three$event_name)
# Normalize the transition matrix
normalized_transitions <- prop.table(as(transitions, "matrix"), margin = 1)
mc <- new("markovchain", transitionMatrix = as(normalized_transitions, "matrix"))
mc
# Print the transition matrix
mc

# Calculate the steady-state distribution
steady_state <- steadyStates(mc)
steady_state
```

```{r}
#Markov Chain Model For Stage
# Create a transition matrix
#transitions <- table(data_three$stage, lag(data_three$stage))
#rownames(transitions) <- colnames(transitions) <- unique(data_three$stage)
# Normalize the transition matrix
#normalized_transitions <- prop.table(as(transitions, "matrix"), margin = 1)
#mc <- new("markovchain", transitionMatrix = as(normalized_transitions, "matrix"))
#mc
# Print the transition matrix
#mc

# Calculate the steady-state distribution
#steady_state <- steadyStates(mc)
#steady_state
```