---
title: "eda"
output: html_document
date: "2024-01-18"
---

1.Where is the fall-off point in the funnel? Where do people usually get stuck in their
journey and as a result don’t become activated users? How does time relate to users not
moving forward in their journey?

2. How can we group customers together such that we find patterns of incompletion in the
journey?

```{r}
#Read in Data and Libraries
library(tidyverse)
library(lubridate)
library(zoo)
data <- read.csv("/Users/yusei/OneDrive/Documents/M148/export.csv")
event_def <- read.csv("/Users/yusei/OneDrive/Documents/M148/Event Definitions.csv")
```

```{r}
#To answer EDA
combinations <- data %>% group_by(customer_id, account_id) %>% count()
cust <- combinations %>% select(customer_id, account_id) %>% group_by(customer_id) %>%  count()
df <- data.frame(cust)
df <- df[df$n != 1,]
print(nrow(df))
acct <- combinations %>% select(customer_id, account_id) %>% group_by(account_id) %>%  count()
df2 <- data.frame(acct)
df2 <- df2[df2$n != 1,]
print(nrow(df2))
```
 
```{r}
#Clean defenitions for cleaner merge
event_def <- event_def %>% select(!c(journey_id, event_definition_id))

#Left Join 
data_def <- left_join(data, event_def, by = 'event_name')
head(data_def, 200)
```

```{r}
#removing duplicate entries that are at the same exact time stamp
data_def <- data_def %>% group_by(customer_id, event_name) %>% filter(event_timestamp != lag(event_timestamp, default="1"))
data_def <- data.frame(data_def)

#Cleaning time to lubridate time
data_def$event_timestamp <- ymd_hms(data_def$event_timestamp)
```

3. Where is it effective to intervene with an email or promotion code
```{r}
#Cleaning duplicate promotion created entries
data_three <- data_def
data_three %>% filter(event_name == 'promotion_created')
head(data_three, 100)
```

Whats rate of success after promo sent? 
```{r}
#want customers who have received promotions. 
#group into customer id, select customer ids where event_name == promotion created
#promos <- data_three %>% group_by(customer_id)

#data_three %>% group_by(customer_id) %>% mutate(time_diff = event_timestamp - lag(event_timestamp, default="1"))

#data_three %>% group_by(customer_id) %>% mutate(diff_between = as.vector(diff(zoo(event_timestamp), na.pad=TRUE)))

#promos[promos$event_name == 'promotion_created'|promos$event_name == 'order_shipped',]

#lag(data_def$event_timestamp)
```

